% \documentclass[../main.tex]{subfiles}
\pagenumbering{roman}
% \begin{document}
\begin{center}
    \Large{\textbf{ACKNOWLEDGMENT}}\\
\end{center}
\vspace{1cm}

First and foremost, I would like to express my sincere gratitude to subject teachers at Hanoi University of Science and Technology for their continuous guidance throughout my study, especially ones from School of Information and Communication Technology. During the past three and a half years, I have learnt from them needed knowledge for pursuing later stages in my Computer Science journey.

I thankfully acknowledge the support of Prof. Huynh Thi Thanh Binh, who accepted me into MSO Lab and {\color{blue}guided me in the first steps of research career.}. My appreciation also extends to my laboratory colleagues, I'm very happy to have had the opportunity to collaborate with all of you, especially M.Sc. Tran Ba Trung, who introduced and invited me to joint work with him in our very first theoretical topic. I would also like to send my sincerity to other members of MSO Lab, Dr. Nguyen Thi My Binh, M.Sc. Nguyen Hong Ngoc, Tran Cong Dao and Tran Huy Hung. Dr.Binh and M.Sc Ngoc supported me a lot when I first joint our lab. Brothers Dao and Hung lent a hand to review my thesis. 

I also cherish the moment doing my thesis under the supervision of Dr. Tran Vinh Duc. Though the time is short, but his style in research inspired me so much. 

Taking my first step on doing theoretical research, I owe a great debt of gratitude to Dr. Ta Duy Hoang (ENS de Lyon) and Dr. Vu Van Khu (National University of Singapore) for training and mentoring me during the working on various problems including ones in this thesis. Without their support (both professional and personally), it would not have been possible for this work to progress as far as it has. 

I'm also grateful to FPT Young Talent's members, especially Do Hoang Khanh, Lai Ngoc Tan and Thanh La. I'll always remember the late night we've spent together sharing out stories and our plans. I had known the way to find my answer for "Who am I going to be? How do I want to live in the next 10 years? 20 years?$\ldots?$" since that night.

% During my four year of university, I'm also engaged to FPT Young Talents (FYT) and Bach Khoa Street Workout Team (BKSW). In FYT, my gratitude goes to Do Hoang Khanh, Lai Ngoc Tan and Thanh La. I'll always remember the late night we've spent together sharing out stories and our plans. I had known the way to find my answer for "Who am I going to be? How do I want to live in the next 10 years? 20 years?$\ldots?$" since that night. 
In Bach Khoa Street Workout, my gratitude goes to Xuan Nam, Duc Anh and Thanh Hai. We've trained and shared our experiences in SW, life and  work as brothers. 

% They not only helped me with mastering high level Street workout's moves, but also with life, works.

My student's life must be harder without the following idiots: Phan Viet Hoang, Phi Phuc , Khanh Doan, Ng Duc Long, Tran Anh, Ba Tan and Hong Sang. They are my best friends in the last four years.

I'm also very grateful to my aunt Hang and uncle Lich, who always look after me just like my mom and dad. 

Last but not least, this thesis is dedicated to my parents for the two decades of your love and support. I would not have come this far without your loving weight behind me.
% \end{document}