A de Bruijn sequence, or a positioning sequence, (of order $k$) is a binary sequence in which every possible length-$k$ string appears exactly once as a substring. The uses of de Bruijn sequences have been found in various fields. Recently, a novel application of positioning sequences has been found in quantum communication by \citeauthor{zhang2021timing}. They adopt such sequences into \gls{HdB} sequences to develop a system for synchronizing in quantum channels. Though having shown advantages against other methods~\cite{zhang2021timing}, such implementation still has drawbacks and there is room for improvements. This thesis focuses on designing a new constrained de Bruijn sequence and proving its efficiency against \gls{HdB} sequence. 

Chapter \ref{chapter:motivation} first briefly introduces the \gls{qkd} protocol, along with the reasonable motivation to study the synchronization mechanisms in satellite quantum channels. Among such mechanisms, the timing and synchronization system proposed by \citeauthor{zhang2021timing} in~\cite{zhang2021timing} is analyzed to recognize its disadvantages. The main results of this thesis, which aim to improve those weaknesses, are summarized. The organization of the whole thesis is given at the end of this chapter. 

% Chapter \ref{chapter:motivation} introduces a de Bruijn based system used in Quantum communication. The drawback of this system is the inspiration for the results in this thesis. This thesis's contributions are also summarized in this chapter. 

\section{Timing and synchronization system in quantum channels}
\input{sections/motivation/dBTS}

\section{The contributions and organization of this thesis}
\input{sections/motivation/contributions}

% Chương này có độ dài không quá 10 trang. Chương này sinh viên trình bày về phân tích rõ ngữ cảnh bài toán cũng như các kết quả nghiên cứu tương tự. Đồng thời, sinh viên có thể trình bày thêm về các kiến thức nền tảng.

% \section{Scope of Research}
% \ldots

% \section{Related Works}
% Trong phần này sinh viên trình bày các nghiên cứu liên quan (related work), chú ý phân tích rõ những ưu nhược điểm của chúng. Từ đó, nêu bật lên động lực để thực hiện nghiên cứu của đồ án này.


% \section{Tên của kiến thức nền tảng số 1}
% Tiêu đề và nội dung của chương này sẽ thay đổi tuỳ thuộc vào từng đồ án. Chú ý trình bày những kiến thức có liên quan mật thiết nhất đối với đồ án của mình, Tránh trình bày lan man những kiến thức phổ thông không cần thiết. 

% \section{Tên của kiến thức nền tảng số 2}
% Tiêu đề và nội dung của chương này sẽ thay đổi tuỳ thuộc vào từng đồ án. Chú ý trình bày những kiến thức có liên quan mật thiết nhất đối với đồ án của mình, Tránh trình bày lan man những kiến thức phổ thông không cần thiết. 